A Fully Decentralized Infrastructure for Subscription-based IoT Data Trading

### 2020-07-31 paper.tex
Add more description of why not IPFS in Chap3

Filecoin \cite{FileCoin} in Inter-Planetary File system (IPFS) is an incentive layer to incent nodes to provide storage. IPFS is a content-based addressing storage model in a peer-to-peer network, which users can obtain the data with the unique hash value through the network. Furthermore, considering the data may loss in the network, IPFS provides \textbf{pin} command for users to store the contents locally that will not be removed. However, the IoT sensor devices have limited space which is not appropriate to preserve generated data. Also, users can have a hard time finding the contents quickly if data is not widely available, the large amount of IPFS nodes and contents. Thus, several pinning services like Pinata provide multiple IPFS nodes around the world to pin users' contents and charge by the size and replicas of contents, and users can even join the dedicated network to speed up the retreiving process.

@@

@@

\subsection{Launch a Refund}
Data subscription is a high risk which data provider may not upload data as the agreement set after receiving the subscription fee. Therefore, in our proposed architecture, data consumers can trigger a refund procedure by sending a transaction on Ethereum if the data is not available or defective. When the refund procedure is launched, all consumers vote to decide whether the refund is established. See Fig.~\ref{fig:refund}. Once the ratio of consent votes of refunding is higher than a threshold, the subscription fee is proportionally transferred to the data provider, broker and every consumer as following, where $N$ is the number of consumers in this contract:

>>>>

Filecoin \cite{FileCoin} in Inter-Planetary File system (IPFS) is an incentive layer to incent nodes to provide storage. IPFS is a content-based addressing storage model in a peer-to-peer network, which users can obtain the data with the unique hash value through the network. Furthermore, considering the data may loss in the network, IPFS provides \textbf{pin} command for users to store the contents locally that will not be removed. However, the IoT sensor devices have limited space which is not appropriate to preserve generated data. Also, users can have a hard time finding the contents quickly if data is not widely available, the large amount of IPFS nodes and contents. Thus, several pinning services like Pinata provide multiple IPFS nodes around the world to pin users' contents and charge by the size and replicas of contents, and users can even join the dedicated network to speed up the retreiving process. Nevertheless, the efficiency problems still occur if the dedicated network grows larger.

@@

Currently, considering the efficiency of uploading large files, IPFS performs better than MAM (i.e., writing contents to IOTA network). However, IOTA network scales when more users and transactions join, and the MAM operations can be delegated to powerful proxy servers which is illustrated in Section.~\ref{section:ta_endpoint}. Furthermore, adopting IPFS in IoT scenarios may meet the challenges of data loss and data retreiving efficiency.

@@

\subsection{Launch a Refund}
\label{section:refund}
Data subscription is a high risk which data provider may not upload data as the agreement set after receiving the subscription fee. Therefore, in our proposed architecture, data consumers can trigger a refund procedure by sending a transaction on Ethereum if the data is not available or defective. When the refund procedure is launched, all consumers vote to decide whether the refund is established. See Fig.~\ref{fig:refund}. Once the ratio of consent votes of refunding is higher than a threshold, the subscription fee is proportionally transferred to the data provider, broker and every consumer as following, where $N$ is the number of consumers in this contract:
